\section{Conclusion}\label{sec-conclude}

In this paper we introduced a new technology that can make it easier for 
researchers to take advantage of of the rich data gathering potential of 
portable devices.  By enabling programmable enforcement of IRB-approved privacy 
policies through the control of sensor access, Sensibility Testbed is able to greatly 
reduce the workload on researchers who no longer need to have a "hands-on"
role in policy enforcement. Based on a study of the literature, Sensibility Testbed
can protect device owners from most of the security and privacy issues identified
 in previous projects using mobile devices. The greatly reduced risk of participation
 for device owners thus encourages the development of a larger and more diverse pool 
 of test subjects. 


For researchers, Sensibility Testbed not only offers a larger and more diverse pool
of test subjects, but also simplifies both the application for, and implementation
of IRB policies for their deployed experiments. Other benefits include the ability to
run multiple experiments simultaneously on the same devices
at the same time with no cross-over between projects, as well as the opportunity to 
reuse experimental set-ups, and easily share data with other researchers.
 
 Based on a study of the literature, Sensibility Testbed can protect device owners
 from most of the security and privacy issuesidentified in previous projects
 using mobile devices. Deployments of the testbed are currently underway and
 additional information about the security effectiveness of the process will
 be forthcoming in the months ahead.\lois{Not sure about this last sentence. 
 Do we want to commit to any type of future action?}
 

